---
title: "Project 3 - Example Main Script"
author: "Yuting Ma, Tian Zheng with updates by Cindy Rush"
date: "February 2, 2018"
output:
  pdf_document: default
  html_document: default
---

### Step 0: Install Required Packages & Specify Directories

```{r, warning = FALSE}
if(!require("EBImage")){
  source("https://bioconductor.org/biocLite.R")
  biocLite("EBImage")
}

if(!require("JOUSBoost")){
  install.packages("JOUSBoost")
  devtools::install_github("molson2/JOUSBoost")
}

if(!require("pbapply")){
  install.packages("pbapply")
}

if(!require("tensorflow")){
  install.packages("tensorflow")
}

if(!require("reticulate")){
  install.packages("reticulate")
}

library("EBImage")
library("JOUSBoost")
library("tidyverse")
```

Directories for training and test data.

```{r}
experiment_dir <- "../data/pets/" # This will be modified for different data sets.
# This is where my data lives (outside of Spring2018)
img_train_dir  <- paste(experiment_dir, "train/", sep="")
img_test_dir <- paste(experiment_dir, "test_practice/", sep="")
```

### Step 1: Set up controls for model evaluation.

```{r exp_setup}
run.cv            <- TRUE # run cross-validation on the training set
K                 <- 5    # number of CV folds
run.feature.NN.train <- TRUE # process features for training set
run.test          <- TRUE # run evaluation on an independent test set
run.feature.NN.test  <- TRUE # process features for test set
```

### Step 2: Read Training Data Labels.

```{r train_label}
label_train <- read.table(paste(experiment_dir, "train_label.txt", sep = ""), header = F)
label_train <- as.numeric(unlist(label_train) == "dog")
```


### Step 3: Training Part

* Extract features for training data.

```{r feature}
source("../lib/feature.R")

NUM_FILES = 2000

# Neural Network Features
tm_NN_feature_train <- NA
if(run.feature.NN.train){
  tm_NN_feature_train <- system.time(NN_train_feature <- NN_feature(img_train_dir, NUM_FILES))
}

save(NN_train_feature, file = "../output/features/NN_train_feature.RData")
```

* Load training functions from "../lib/train.R".

```{r loadlib}
source("../lib/train.R")
source("../lib/test.R") # for cross validation
```

* AdaBoost Model cross validation.

```{r runcv, message=FALSE, warning=FALSE}
source("../lib/cross_validation.R")

if (!exists("NN_train_feature")) {
  load("../output/features/NN_train_feature.RData")
}

model_values <- seq(3, 11, 2)
model_labels <- paste("Adaboosting with tree depth =", model_values)


#Adaboosting label need to be -1 and 1, so made some transformation here
label_trainada<-label_train
label_trainada[which(label_trainada==0)] <--1

if(run.cv){
  err_cv <- array(dim = c(length(model_values), 2))
  for(k in 1:length(model_values)){
    cat("k=", k, "\n")
    err_cv[k,] <- cv.function.ada(NN_train_feature, label_trainada, model_values[k], K)
  }
  save(err_cv, file = "../output/err_cvNN_Ada.RData")
}
```

* Visualize the cross-validation results. 

```{r cv_vis}
if(run.cv){
  if (!exists("err_cv")) {
    load("../output/err_cvNN_Ada.RData")
  }
  # pdf("../figs/cv_results_NN_ada.pdf", width=7, height=5)
  plot(model_values, err_cv[,1], xlab = "Tree Depth", ylab = "CV Error",
       main = "Cross Validation Error", type = "n", ylim = c(0, 0.15))
  points(model_values, err_cv[,1], col = "blue", pch=16)
  lines(model_values, err_cv[,1], col = "blue")
  arrows(model_values, err_cv[,1] - err_cv[,2], model_values, err_cv[,1] + err_cv[,2], 
        length = 0.1, angle = 90, code = 3)
  # dev.off()
}
```

* Choose the "best" parameter value

```{r best_model}
model_best <- model_values[1]
if(run.cv){
  model_best <- model_values[which.min(err_cv[, 1])]
}

par_best <- list(depth = model_best)
```

* Train the model with the entire training set using the selected model (in this case, model parameter) via cross-validation.

```{r final_train}
tm_train <- NA
tm_train <- system.time(fit_train_ada <- ada_train(NN_train_feature, label_trainada, par_best))
save(fit_train_ada, file = "../output/models/NN_Ada_fit_train_model.RData")
```

### Step 4: Testing Part

* Extract features from test data

```{r feature}
source("../lib/feature.R")

NUM_TEST_FILES = 1850

# Neural Network Features
tm_NN_feature_test <- NA
if(run.feature.NN.test){
  tm_NN_feature_test <- system.time(NN_test_feature <- NN_feature(img_test_dir, NUM_TEST_FILES))
}

save(NN_test_feature, file = "../output/features/NN_test_feature.RData")
```

* Make predictions with pre-saved model


```{r test}
source("../lib/test.R")
tm_test <- NA
if(run.test){
  if (!exists("fit_train_ada")) {
    load(file = "../output/models/NN_Ada_fit_train_model.RData")
  }
  if (!exists("NN_test_feature")) {
    load(file = "../output/features/NN_test_feature.RData")
  }
  tm_test <- system.time(pred_test <- ada_test(fit_train_ada, NN_test_feature))
  save(pred_test, file = "../output/predictions/pred_NN_Ada_test_practice.RData")
}
```

* Check accuracies

```{r}
# test_label = label_train[1:1850]
# accu = mean(test_label == pred_test)
```

### Summarize Running Time


```{r running_time}
cat("Time for constructing training features=", tm_NN_feature_train[1], "s \n")
cat("Time for constructing testing features=", tm_NN_feature_test[1], "s \n")
cat("Time for training model=", tm_train[1], "s \n")
cat("Time for making prediction=", tm_test[1], "s \n")
```
